---
title: "Car Insurance Claim Prediction Analysis"
output: html_document
---

# Car Price Prediction Using Linear Regression

## Overview
### This project analyzes car insurance customer data to predict whether a customer will file a claim. We build simple logistic regression models using individual features and identify the best predictor based on accuracy.

## Load Libraries and Data

```{r}
# Load required libraries
library(readr)  
library(dplyr)  
library(glue)  
library(yardstick)  

# Load the datasets
car_data <- read_csv("car_insurance.csv", show_col_types = FALSE)

# Display initial few rows and the structure of the data  
print(head(car_data))  
str(car_data)  
```

## Data Cleaning
```{r}
# Clean the data:  
# - Remove rows with any missing values  
# - Remove the "id" column  
clean_data <- car_data %>%    
  na.omit() %>%    
  select(-id)  
  
# Convert outcome to factor since it is the target variable (binary)  
clean_data <- clean_data %>%    
  mutate(outcome = as.factor(outcome))  
  
# Show dimensions of cleaned data  
cat("Cleaned data dimensions: ", dim(clean_data)[1], "rows and", dim(clean_data)[2], "columns\n")  
```

## Model Building
```{r}
# Get the list of features (all columns except 'outcome')  
feature_names <- setdiff(names(clean_data), "outcome")  
  
# Initialize data frame to store accuracy results for each feature  
results <- data.frame(feature = character(), accuracy = numeric(), stringsAsFactors = FALSE)  
  
# Loop over features to build single variable logistic regression models  
for(feature in feature_names) {  
    # Create formula: outcome ~ feature  
    current_formula <- as.formula(glue("outcome ~ {feature}"))  
      
    # Fit logistic regression  
    model <- glm(current_formula, data = clean_data, family = binomial)  
      
    # Predict probabilities  
    preds_prob <- predict(model, type = "response")  
      
    # Classify with threshold 0.5  
    preds_class <- ifelse(preds_prob >= 0.5, 1, 0) %>%   
      factor(levels = levels(clean_data$outcome))  
      
    # Calculate accuracy using yardstick  
    temp_df <- tibble(truth = clean_data$outcome, prediction = preds_class)  
    acc <- accuracy(temp_df, truth = truth, estimate = prediction)$.estimate  
      
    # Append result  
    results <- rbind(results, data.frame(feature = feature, accuracy = acc,  
                                         stringsAsFactors = FALSE))  
}  
  
# Sort results by accuracy in descending order  
results <- results %>% arrange(desc(accuracy))  
  
# Print all features' accuracy results  
print(results)  
```

## Identify Best Performing Feature
```{r}
# Identify the best performing feature and its accuracy  
best_result <- results %>% filter(accuracy == max(accuracy))  
best_feature_df <- best_result %>% rename(best_feature = feature, best_accuracy = accuracy)  
print(best_feature_df)  
```
